### 2017-11-03 manuscript.rmd
minor changes, new pdf (commented out ape::rotate(ultratree, 31) )

	summary_stats = read.table("Library_summary.csv", header=TRUE, sep=",")
	names(summary_stats)<-c("Species","Mean insert size (bp)","Insert size standard deviation","Number of read pairs","Percent kept after rRNA removal","Percent kept after assembly","Adapter fails","Quality fails","Base Composition fails","Total assembled transcripts","Coding transcripts")
	specimen_data = read.csv("Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")
```

@@

Stefan Siebert^1,2^, Felipe Zapata^1,3^, Mark Howison^4^, Cat Munro^1^, Alejandro Damian Serrano^1^, Samuel H Church^1, 5^, Freya Goetz^1,5^, Phil Pugh, Steven H.D. Haddock^4^, Casey W. Dunn^1^*

^1^ Department of Ecology and Evolutionary Biology, Brown University, Providence, RI, USA

^2^ Current address: Department of Molecular & Cellular Biology, University of California at Davis, Davis, CA, USA

^3^ Current address: Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA, USA

^4^ Brown Data Science Practice, Brown University, Brown University, Providence, RI, USA

^5^ Harvard

^5^ Current address: Smithsonian, Washington DC, USA

^4^ Monterey Bay Aquarium Research Institute, Moss Landing, CA, USA

>>>>

	summary_stats = read.table("supplementary_info/Library_summary.csv", header=TRUE, sep=",")
	names(summary_stats)<-c("Species","Mean insert size (bp)","Insert size standard deviation","Number of read pairs","Percent kept after rRNA removal","Percent kept after assembly","Adapter fails","Quality fails","Base Composition fails","Total assembled transcripts","Coding transcripts")
	specimen_data = read.csv("supplementary_info/Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")
```

@@

Catriona Munro^1^, Stefan Siebert^1,2^, Felipe Zapata^1,3^, Mark Howison^4^, Alejandro Damian Serrano^1,9^, Samuel H Church^1, 5^, Freya Goetz^1,6^, Phil Pugh^7^, Steven H.D. Haddock^8^, Casey W. Dunn^1,9^*

^1^ Department of Ecology and Evolutionary Biology, Brown University, Providence, RI 02912, USA

^2^ Current address: Department of Molecular & Cellular Biology, University of California at Davis, Davis, CA 95616, USA

^3^ Current address: Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA

^4^ Brown Data Science Practice, Brown University, Brown University, Providence, RI 02912, USA

^5^ Department of Organismic and Evolutionary Biology, Harvard University, Cambridge, MA 02138, USA

^6^ Current address: Smithsonian Institution, National Museum of Natural History, Washington, DC 20560, USA

^7^ National Oceanography Centre, Southampton, SO14 3ZH, UK

^8^ Monterey Bay Aquarium Research Institute, Moss Landing, CA 95039, USA

^9^ Current address: Department of Ecology and Evolutionary Biology, Yale University, New Haven, CT 06520, USA
